Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2016-10-24 paper.tex
update

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. An optimisation problem is another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems. This paper develops a more applicable approach for comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

@@

\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}. Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research. Those semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition are often addressed regarding the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts by the semantic level of web service composition. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match making as web service composition solutions. For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.

The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements. Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation. We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field. Three objectives of this work are accomplished as follows:

@@

 \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate optimised comprehensive quality awareness solution.

 \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are composed as the following: Sect. \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect. \ref{qswsc_approach} represents the an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and the whole implementation algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of these experiments; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable composite quality of service. To accomplish the composte goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated a output set: $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$ with found services output. The Output Set is used to further discovery all related services until the desired $T_{Output}$ found in the updated Output Set. It normally results in more than one solutions. Service selection is to select one of those composite solution considering closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach},

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service matching process is to pair the output and input concepts of two services according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ are defined in.

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected with calculation of matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web service is performed over the PSO in subSect. \ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for building a graph. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services. In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

@@

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition, this overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of matchmaking for service selection are not considered.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}. Match type is considered to be one factor for the semantic quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services with close semantic matching. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.

@@

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite goal. The non-functional properties typically refer previously discussed QoS, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{smq})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.

@@

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Generally, web services could have more than one concept-related parameters. In semantic matchmaking process, two levels of quality aggregation are considered --- edge level and construct level. At edge level, the edge-level quality aggregation is determined by the mean of concept-related parameter quality in both $q(s_{mt})$ and $q(s_{s})$ respectively. Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1}, which is a quality aggregate matrix for semantic web service composition. Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and $q(s_{s})$ respectively. The QoS aggregation $Q(q_{QoS})$ calculation is same to \cite{cardoso2004quality}.

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value result falls within 0 to 1. Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.

@@

 \caption{Steps of graph-based PSO optimisation technique.}
\label{psoSteps}
\end{algorithm}
The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model. The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, so finding the best fitness of the composite service solution is to discover the optimised location of the particle. In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order. Later on, we decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node. We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept being updated using outputs from new-added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building. In addition, dangle service nodes and edges should be removed. The particle's fitness value can be calculated by the graph-based composition solution. In the evolutionary process, pBest and gBest value are assigned and updated in each generation while swarm's position is updated. Finally, we return the graph G built in the last iteration as the optimised solution.

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and to explore the impact of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} web service data sets to perform a standard evaluation. WSC09 designed OWL for providing richer semantics consisting tasks with variable size. With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services of each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are flexibly defined by users' preferences. As part of their requirement, we configure weights of fitness function as the same to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.

\section{Results and Analysis}\label{results_analysis}
\subsection{Convergence Test}\label{convergenceTest}
To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section. We show the convergency of five tasks in WSC09. To further study an overall effectiveness of evaluation model and investigate the impacts of all involved components in the fitness function. We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{convergency.pdf}}}
 \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
 \label{exp_fitnessvalue}
\end{figure}

>>>>

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. Optimisation problems are another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems. This paper develops a more applicable approach for measuring comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

@@

\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems --- diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}. Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research. This semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition are often addressed regarding the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts by the semantic level of web services. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match making as web service composition solutions. For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.

The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements. Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation. We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field. Three objectives of this work are accomplished as follows:

@@

 \item To apply PSO for implementing comprehensive awareness automated semantic web service composition. PSO sorts out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate a final solution.

 \item To explore the performance of comprehensive quality awareness semantic web service composition, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are composed as the following: Sect. \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect. \ref{qswsc_approach} represents the an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and the whole implementation algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of the experiment; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. Meanwhile, a output set is initialised and updated with found services output, which could be denoted as  $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output Set is used to discovery all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one solutions. Service selection is to select one of those composite solution considering the closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach},

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service matching process is to pair the output and input concepts of two services according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ are defined in.

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web services is performed over the PSO algorithm in subSect. \ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking}

The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self}, which could be considered to be an alternative form of ontology for services. In ontology, semantics specifies the both concepts and individuals in the terms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

@@

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}. Match type is considered to be one factor for the semantic matchmaking quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new} --- a taxonomy-based measurement for ontology matching. In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.

@@

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite goal. The non-functional properties typically refers to previously discussed QoS, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{sm})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.

@@

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Generally, web services could have more than one concept-related parameters. In semantic matchmaking process, two levels of quality aggregation are considered --- edge level and construct level. At edge level, the edge-level quality aggregation is determined by the mean value of concept-related parameter quality in $q(s_{mt})$ and $q(s_{s})$ respectively. Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1} --- a quality aggregate matrix for semantic web service composition. Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and mean function of edge-level $q(s_{s})$ respectively. The QoS aggregation $Q(q_{QoS})$ calculation is same to \cite{cardoso2004quality}.

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregated value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst. As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within 0 to 1. Also, the lowest T and C value represent the best conponent quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.

@@

 \caption{Steps of graph-based PSO optimisation technique.}
\label{psoSteps}
\end{algorithm}
The overall algorithm investigated here is a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model. The idea is to translate the particle location into a service queue as an indirect representation of graph-based service composition, so finding the best fitness of the composite service solution is to discover the optimised location of the particle. In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, and all the services index is mapped to the location in a particle, and we put services in a queue in ascending order, from which we decode a corresponding graph using a forward graph-building technique. The particle's fitness value can be calculated based on that built graph. During the evolutionary process, pBest and gBest value are assigned and updated in each generation with new-updated particles' position while graph-based solutions are generated at the same time. eventually, we return the graph built from the last generation as an optimised solution. In the forward graph building algorithm. We select and connect web services to the startNode from the service queue if the web service can satisfy the given $T_{input}$. Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added web services in the graph, later on, more services are connected if services' inputs could be satisfied by any output in the Output Set. At last, The end node is connected if the updated Output Set contains the $T_{output}$. In addition, dangle service nodes and edges should be removed.

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, and to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a standard evaluation. WSC09 provides problems,  WSDL+MECE, taxonomy files in formats of xml, xml, and owl respectively, where five tasks consisted in with variable size in both services, and ontologies. Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are flexibly defined by users' preferences. As part of their requirement, we configure weights of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.

\section{Results and Analysis}\label{results_analysis}
\subsection{Convergence Test}\label{convergenceTest}

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{convergency.pdf}}}
 \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
 \label{exp_fitnessvalue}
\end{figure}

To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section to investigate the convergency of five tasks in WSC09. To further study an overall effectiveness of evaluation model and impacts of all involved components in the fitness function. We analysis all the performances of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.

Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs. The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes. The same behaviour is observed over the rest tasks. Also, there is a fast convergence of the fitness value that be observed. That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.
